Online {\IterComp}

### 2017-11-14 motivation.tex
small udpdates to motivation

    \paragraph{Iterative compilation needs representative inputs.} 
    In order to highlight what happens when we apply iterative compilation using the wrong set of inputs, we selected two distinct sets of
    10 out of the 1,000 inputs of the of \textit{KDataSets}~\cite{chen10,chen12a} for the \texttt{tiff2bw} benchmark.
    The first set represents the training set, i.e., the set of inputs that will be used for selecting the best optimization sequence by
    iterative compilation, and the second set is a specific set of inputs which is misrepresented by the training set.
    After performing iterative compilation on the first set, the selected optimization sequence has an average speedup of 1.22 over -O3 for
    the training set itself, but it produces a slowdown of 0.91 for the second set of inputs.
    However, if the iterative compilation was performed on the second set itself, it would be able to find a optimization sequence that
    produces a speedup of 1.07 over -O3.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth]{figs/motivation_wrong_inputs.pdf}
    \caption{Iterative compilation performed on the wrong set of inputs compared to the ideal case for the \texttt{tiff2bw} benchmark.}
    \label{fig:motivation_wrong_inputs}
\end{figure}

>>>>

    \paragraph{Iterative compilation needs representative inputs.} 
    Figure~\ref{fig:motivation_wrong_inputs} highlights what happens when we apply iterative compilation using the wrong set of inputs, we selected two distinct sets of
    10 out of the 1,000 inputs of the of \textit{KDataSets}~\cite{chen10,chen12a} for the \texttt{tiff2bw} benchmark.
    The first set represents the training set, i.e., the set of inputs that will be used for selecting the best optimization sequence by
    iterative compilation, and the second set is a specific set of inputs which is misrepresented by the training set, let us call it the production set.
    After performing iterative compilation on the training set, the selected optimization sequence has an average of 22\% improvement over -O3 for
    the training set itself, but it produces a slowdown of about 9\% for the production set.
    However, in the ideal case, if the iterative compilation was performed on the production set itself, it would be able to find an optimization sequence that
    results on a 7\% improvement over -O3, this is an improvement of about 17\% over
    the result of iterative compilation on the wrong set of inputs.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth]{figs/motivation_wrong_inputs.pdf}
    \caption{Performance results for the \texttt{tiff2bw} benchmark, comparing optimization sequences selected by iterative compilation when performed on the wrong set of inputs and the ideal case using the same set of inputs.
    This result supports the fact that iterative compilation needs representative inputs.}
    \label{fig:motivation_wrong_inputs}
\end{figure}
